---
title: "Radical innovation from a network perspective"
description: |
  Exploring radicalness in patent data using network analysis
author:
  - name: Robert Kalcik
    affiliation: AIT Austrian Institute of Technology
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
library(tidyverse)
library(countrycode)
library(tidygraph)
library(igraph)
library(ggraph)

```

# Load data

Load patent-inventor data and select all patents with at least one inventor within the EU28.

```{r}
df_inv <- readRDS("../data/regpat_epo_inv.rds")

```

# Geographic distance

## Cooccurence of regions

Explore cooccurence of inventor regions on individual patent applications

```{r}
cooc <- df_inv %>% 
  widyr::pairwise_count(reg, appln_id) %>% 
  rownames_to_column(var = "id")
cooc %>% arrange(desc(n))
```

## Distance

Distance between existing region pairs

```{r}
cent <- readRDS(file = "../data/centroids_EU.rds")
world <- readRDS(file = "../data/centroids_world.rds")

dist <- cooc %>% select(-n) %>% 
  gather(key, reg, -id) %>% select(-key) %>% 
  left_join(cent, by = "reg") %>% 
  mutate(ctry = str_sub(reg, 1, 2)) %>% 
  left_join(world, by = "ctry") %>% 
  mutate(
    lat = case_when(
      !is.na(lat.x) ~ lat.x,
      TRUE ~ lat.y
    ),
    lon = case_when(
      !is.na(lon.x) ~ lon.x,
      TRUE ~ lon.y
    )
  ) %>% 
  select(id, lon, lat) %>% 
  filter(!is.na(lat))

dist <- dist %>% 
  group_by(id) %>% nest() %>% 
  mutate(dist = map_dbl(data, ~ geosphere::distGeo(.x)[1]))

cooc <- cooc %>% left_join(dist %>% select(-data), by = "id")

```

# Region network 

Compute social proximity between regions. 

```{r}
g <- graph_from_edgelist(
    cooc %>% select(item1, item2) %>% as.matrix(), 
    directed = FALSE
  ) %>% 
  as_tbl_graph() %>% 
  mutate(id = row_number())
  
g <- g %>% activate(edges) %>% 
  distinct()%>% 
  left_join(as_tibble(g), by = c("from" = "id")) %>% 
  left_join(as_tibble(g), by = c("to" = "id")) %>% 
  left_join(cooc, by = c("name.x" = "item1", "name.y" = "item2")) 

g <- g %>% 
  activate(nodes) %>% 
  # mutate(central = centrality_alpha(), between = centrality_betweenness())
  left_join(df_inv %>% count(reg), by = c("name" = "reg"))

saveRDS(g, "data/graph.rds")
```

## Visualise

```{r}
# viz ---------------------------------------------------------------------
nuts <- read_delim("../data/REGPAT/REGPAT_REGIONS.txt", delim = "|")
  
g_aut <- g %>% activate(nodes) %>% 
  filter(str_sub(name, 1, 2) == "AT") %>% 
  left_join(nuts, by = c("name" = "reg_code"))

g_aut %>%
  # ggraph(layout = "graphopt") + 
  # ggraph(layout = 'linear', circular = TRUE) +
  ggraph() +
  geom_edge_link(aes(width = n), alpha = 0.2) + 
  scale_edge_width(range = c(0.2, 2)) +
  geom_node_point(aes(size = n, colour = Up_reg_label)) +
  geom_node_text(aes(label = reg_label), repel = TRUE) +
  labs(edge_width = "# Co-Patents", node_size = "# Total Patents") +
  theme_graph()

```

# Merge

Aggregate data to the patent level and merge inventor and applicant data

```{r}
ipc <- readRDS("../data/ipc.RDS")
radical <- readRDS("../data/radical.RDS")

df_patent <- df_inv %>% 
  select(appln_id, year_app, reg) %>% 
  distinct() %>% 
  group_by(appln_id, year_app) %>% 
  nest()

df_patent <- df_patent %>% left_join(df_avg_dist, by = c("appln_id"))
df_patent <- df_patent %>% left_join(as_tibble(g), by = "reg")
df_patent <- df_patent %>% replace_na(list(avg_dist = 0, d = "Same Region"))
df_patent <- df_patent %>% left_join(avg_similarity, by = "appln_id")

# anlysis -----------------------------------------------------------------
df_patent <- df_patent %>% 
  mutate(
    avg_dist_sqr = avg_dist ^2,
    similarity_unity = case_when(is.na(similarity) ~ 1, TRUE ~ similarity)
  )

saveRDS(df_patent, file = "data/regression_in.rds")

m1 <- lm("radicalness ~ avg_dist + avg_dist_sqr + avg_central + year + factor(tech_field) ", df_patent)
summary(m1)

m2 <- lm("radicalness ~ factor(d) + avg_central + year + factor(tech_field)", df_patent)
summary(m2)

m3 <- lm("radicalness ~ avg_dist + avg_dist_sqr + avg_central + similarity + year + factor(tech_field) ", df_patent)
summary(m3)

m4 <- lm("radicalness ~ factor(d) + avg_central + similarity + year + factor(tech_field)", df_patent)
summary(m4)

m7 <- lm("radicalness ~ avg_dist + avg_dist_sqr + avg_central + similarity_unity + year + factor(tech_field) ", df_patent)
summary(m7)

m8 <- lm("radicalness ~ factor(d) + avg_central + similarity_unity + year + factor(tech_field)", df_patent)
summary(m8)

stargazer::stargazer(m1, m2, m3, m4, m7, m8, type = "html", 
          dep.var.labels = c(), 
          covariate.labels = c(), 
          out="models.htm")


# only radical > 0 --------------------------------------------------------

df_patent_filtered <- df_patent %>% filter(radicalness > 0 )

m1 <- lm("radicalness ~ avg_dist + avg_dist_sqr + avg_central + year + factor(tech_field) ", df_patent_filtered)
summary(m1)

m2 <- lm("radicalness ~ factor(d) + avg_central + year + factor(tech_field)", df_patent_filtered)
summary(m2)

m3 <- lm("radicalness ~ avg_dist + avg_dist_sqr + avg_central + similarity + year + factor(tech_field) ", df_patent_filtered)
summary(m3)

m4 <- lm("radicalness ~ factor(d) + avg_central + similarity + year + factor(tech_field)", df_patent_filtered)
summary(m4)

m7 <- lm("radicalness ~ avg_dist + avg_dist_sqr + avg_central + similarity_unity + year + factor(tech_field) ", df_patent_filtered)
summary(m7)

m8 <- lm("radicalness ~ factor(d) + avg_central + similarity_unity + year + factor(tech_field)", df_patent_filtered)
summary(m8)

stargazer::stargazer(m1, m2, m3, m4, m7, m8, type = "html", 
                     dep.var.labels = c(), 
                     covariate.labels = c(), 
                     out = "models_intensive.htm")

# merge with full data ----------------------------------------------------
person_reg <- df %>% select(reg, person_id, year)
reg_edges <- df %>% select(appln_id, reg) %>% distinct()
reg_edges <- full_join(reg_edges, reg_edges, by = "appln_id")


# node similarity ---------------------------------------------------------
# similarity <- df %>% select(appln_id, reg) %>% 
#   count(appln_id, reg) %>% 
#   widyr::pairwise_delta(appln_id, reg, n, method = "burrows")

s <- reg_edges %>% count(reg.x, reg.y) %>% 
  filter(reg.x != reg.y) %>% 
  group_by(reg.x) %>% mutate(total.x = sum(n, na.rm = TRUE)) %>% ungroup() %>% 
  group_by(reg.y) %>% mutate(total.y = sum(n, na.rm = TRUE)) %>% ungroup() %>% 
  mutate(similarity = n /(total.x + total.y))

avg_similarity <- reg_edges %>% left_join(s, by = c("reg.x", "reg.y"))
avg_similarity <- avg_similarity %>% group_by(appln_id) %>% summarise(similarity = mean(similarity, na.rm = TRUE))


# g %>% activate(node) %>% 
#   mutate(similarity = node_similarity_with())

reg_edges %>% count(reg.x, reg.y)
  widyr::pairwise_delta()
```







